Object-based Auditory Scenes Similarity Retrieval and Classification With Scattering Transforms

### 2016-07-09 paper/structureScene.tex
finish Fig 1

\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{pgf}
\usepackage{tikz}
\usetikzlibrary{arrows,positioning}
\usepackage{url}
\usepackage{color}
\usepackage{graphicx}
\usepackage{xspace}
\newcommand*{\eg}{e.g.\@\xspace}
\newcommand*{\ie}{i.e.\@\xspace}
\newcommand*{\vs}{vs.\@\xspace}

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}

@@

\begin{figure}
\begin{center}
\setlength{\unitlength}{1cm}
\begin{picture}(5,2)
 \put(-1.5,0.0){\includegraphics[height=2cm,width=3.5cm]{gammatone_Q8.png}}
 \put(2.5,0.0){\includegraphics[height=2cm,width=3.5cm]{gammatone_Q1.png}}
\end{picture}
\caption{
\label{fig:gammatones}
Left: Gammatone wavelet $\boldsymbol{\psi_{\gamma_1}}(t)$ with a quality factor of $Q_1=8$.
Right: Gammatone wavelet $\boldsymbol{\psi_{\gamma_2}}(t)$ with a quality factor of $Q_2=1$.
\vl{we should discuss color schemes and axis labels} \ml{yes we should but for the second submission, go ahead}}
\end{center}
\end{figure}

@@

Reducing the frequency range is an effective way to enhance invariance, widely used in the literature.
For instance, \cite{roma2013} achieved the best performance in the 2013 edition of the DCASE challenge, rely on cepstral descriptors computed up to a cutoff frequency as small as $\xi_{1,\max}  = 900\,\mathrm{Hz}$ instead of the more conventional value of $16\,\mathrm{kHz}$.
\vl{Qu'en penses-tu ML ?}
\ml{j'ai un peu reformuler}

>>>>

\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{pgf}
\usepackage{tikz}
\usetikzlibrary{arrows,positioning}
\usetikzlibrary{arrows.meta}
\usepackage{url}
\usepackage{color}
\usepackage{graphicx}
\usepackage{xspace}
\newcommand*{\eg}{e.g.\@\xspace}
\newcommand*{\ie}{i.e.\@\xspace}
\newcommand*{\vs}{vs.\@\xspace}

% correct bad hyphenation here
\hyphenation{wave-let}

@@

\begin{figure}
\begin{center}
\begin{tikzpicture}
\useasboundingbox[red] (-0.25, -0.5) rectangle (8.25, 2);
\node (omlabel1) at (3.5, 1) {$t$};
\draw[-{Latex[length=2mm]}] (0, 1) -- (omlabel1);
\draw[-{Latex[length=2mm]}] (0, 1) -- (0, 2);
\node[anchor=south west,inner sep=0] at (0, 0) {\includegraphics[height=2cm,width=3cm]{gammatone_Q8.png}};
\node at (2, -0.25) {(a)};
\node (omlabel2) at (8, 1) {$t$};
\draw[-{Latex[length=2mm]}] (4.5, 1) -- (omlabel2);
\draw[-{Latex[length=2mm]}] (4.5, 1) -- (4.5, 2);
\node[anchor=south west,inner sep=0] at (4.5, 0) {\includegraphics[height=2cm,width=3cm]{gammatone_Q1.png}};
\node at (6.5, -0.25) {(b)};
\end{tikzpicture}
\caption{
\label{fig:gammatones}
Gammatone wavelets $\psi(t)$ in the time domain with quality factors (a) $Q = 4$ and (b) $Q = 1$. Blue and red oscillations represent the real and imaginary parts. The orange envelope represents the complex modulus.}
\end{center}
\end{figure}

@@

Reducing the frequency range is an effective way to enhance invariance, widely used in the literature.
For instance, \cite{roma2013} achieved the best performance in the 2013 edition of the DCASE challenge, rely on cepstral descriptors computed up to a cutoff frequency as small as $\xi_{1,\max}  = 900\,\mathrm{Hz}$ instead of the more conventional value of $16\,\mathrm{kHz}$.
